Fast Neural Machine Translation Implementation

### 2018-05-18 wnmt.2018/wnmt.tex
small numerical differences

It is tempting to ignore these considerations, for example, by always decoding with a constant batch and beam size and ignoring hypotheses which are not needed but this comes at a cost of lower translation speed due to wasteful processing.

@@

  \ForAll{hypo $h$ in $b'$}
    \If{$h \neq \textless/s \textgreater$  }
      \State Add $h$ to $b$
    \EndIf
  \EndFor
\EndWhile

@@

The efficiency of Amun's batching algorithm can be seen by observing the time taken for each decoding step in a batch of sentence, Figure~\ref{fig:decode-step}. Amun's decoding becomes faster as sentences finish translating. This contrast with the Marian inference engine, which uses a simpler batching algorithm, where the speed stays relatively constant throughout the decoding of the batch.

@@

Using batching can increase the translation speed by over 20 times in Amun, Figure~\ref{fig:batch-size}. Just as important, it doesn't suffer degradation with large batch sizes unlike the simpler algorithm which slows down when batch size over 1000 is used. This scalability issue is likely to rise in importance with new GPUs with ever increasing core counts.

>>>>

It is tempting to ignore these considerations, for example, by always decoding with a constant batch and beam size and ignoring hypotheses which are not needed. Figure~\ref{algo:simple-mini-batching} illustrates a na\"ive mini-batching with a constant size batch. The downside to this algorithm is lower translation speed due to wasteful processing.

\begin{algorithm}
\begin{algorithmic}
\Procedure{Batching}{encoded sentences $i$, beam size $s$}

\State Create batch $b$ from $i$, $s$

\While{hypo $h \neq \textless/s \textgreater, \forall h \in b $ } 
  \State $b$ = DecodeAndBeamSearch($b$)
\EndWhile

\end{algorithmic}
\caption{Na\"ive mini-batching}
\label{algo:simple-mini-batching}
\end{algorithm}

@@

  \ForAll{hypo $h \in b'$}
    \If{$h \neq \textless/s \textgreater$  }
      \State Add $h$ to $b$
    \EndIf
  \EndFor
\EndWhile

@@

The efficiency of Amun's batching algorithm can be seen by observing the time taken for each decoding step in a batch of sentence, Figure~\ref{fig:decode-step}. Amun's decoding becomes faster as sentences finish translating. This contrast with the Marian inference engine, which uses a na\"ive batching algorithm, where the speed stays relatively constant throughout the decoding of the batch.

@@

Using batching can increase the translation speed by over 20 times in Amun, Figure~\ref{fig:batch-size}. Just as important, it doesn't suffer degradation with large batch sizes unlike the na\"ive algorithm which slows down when batch size over 1000 is used. This scalability issue is likely to increase in importance with new GPUs with ever increasing core counts.
